### 2020-10-14 README.Rmd
Internal consistncy changes with large modifications to readzonefile
Modified the datafile formats from the template making functions and the read daat file functions. This will have broken a number of examples but will get to those.

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/run1"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1sm\au2pop6.csv
# and region1.csv file in the data directory
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(6,resdir,filename="zone1sau2pop6.csv")

>>>>

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/run1"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1.csv, and a zone1sau2pop6.csv or population data file 
# in the data directory, which in this case is the same as the resdir
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(numpop=6,resdir,filename="zone1sau2pop6.csv")
